---
title: "Software Failure and Reliability Assessment Tool: Report"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(shiny)
library(DT)
library(knitr)
library(gdata)
library(ggplot2)
library(rootSolve)
library(readxl)
```

```{r, echo=FALSE}
source('~/Downloads/srt-3.core-master/utility/data/Data_Tools.R')

#Input excel file with a single sheet for now
d <- read_excel("~/Downloads/srt-3.core-master/model_testing/model_data.xlsx")
cnames <- colnames(d) # Read column names in the input excel file

#Data conversion depending on the type of the input data
if("FN" %in% cnames && "IF" %in% cnames && "FT" %in% cnames){
  	FT <- d$FT
  	IF <- d$IF
  	FN <- d$FN
}else if("FN" %in% cnames && "IF" %in% cnames){
  	FT <- IF_to_FT(d$IF)
  	IF <- d$IF
  	FN <- d$FN
}else if("FN" %in% cnames && "FT" %in% cnames){
  	IF <- FT_to_IF(d$FT)
  	FT <- d$FT
  	FN <- d$FN
}else if("T" %in% cnames && "FC" %in% cnames && "CFC" %in% cnames){
  FT <- FC_to_FT(d$FC)
  IF <- FT_to_IF(FT)
  FN <- d$T
}else if("T" %in% cnames && "FC" %in% cnames){
  CFC <- FC_to_CFC(d$FC)
  FT <- FC_to_FT(d$FC)
  IF <- FT_to_IF(FT)
  FN <- d$T
}else if("T" %in% cnames && "CFC" %in% cnames){
  FC <- CFC_to_FC(d$CFC)
  FT <- FC_to_FT(d$FC)
  IF <- FT_to_IF(FT)
  FN <- d$T
}else{
  print("Upload your input data/file formatted according to the SFRAT guidelines")
}
#FT
#IF
#FN
#FC
#CFC
```

# Tab 1: Select, Apply, and Analyze Data
Sample of the uploaded input data is shown below: 
```{r, echo=FALSE}
kable(d[1:10,], caption="First ten points of the input data")
```

## Cumulative failures
```{r, echo=FALSE}
plot(FT,FN,type="s", xlab="Cumulative test time",ylab="Cumulative number of failures",main = "Cumuative Failures vs. cumulative test time")
```

## Times between failures
```{r, echo=FALSE}
plot(FT,IF,type="s", xlab="Cumulative test time",ylab="Times between successive failures",main = "Interfailure times vs. cumulative test time")
```

## Failure intensity
```{r, echo=FALSE}
plot(FT,1/IF,type="s", xlab="Cumulative test time",ylab="Number of failures per unit time",main = "Empirical failure intensity vs. cumulative test time")
```

## Laplace Trend Test
```{r, echo=FALSE}
laplace_trend_test <- function(inter_failure)
{
  n <- length(inter_failure)
  failure_time <- IF_to_FT(inter_failure)   
  laplace_trend <- c()
  laplace_trend[1] <- 0
  for(i in 2:n)
  {
    sumint <- 0
    for(j in 1:(i-1))
    {
      sumint <- sumint + failure_time[j]  
    }
    laplace_trend[i] <-(((1/(i-1))*sumint) -(failure_time[i]/2))/(failure_time[i]*(1/(12*(i-1))^(0.5)))
  }
  trend_data <- data.frame(c(1:length(laplace_trend)),laplace_trend)
  names(trend_data) <- c("Index","Laplace_factor")
  return(trend_data)
}
plot(laplace_trend_test(IF),type="s",xlab="Failure number", ylab="Laplace test statistic",main="Laplace trend test")

#This code will enable display of siginificant lines
localTrendPlot <- ggplot()
localTrendPlot <- localTrendPlot + xlab("Failure Number")+ylab("Laplace Test Statistic")
localTrendPlot <- localTrendPlot+ggtitle("Laplace trend test of")
localTrendPlot <- localTrendPlot + geom_hline(yintercept = qnorm(0.1), color="red", alpha=0.8)
localTrendPlot <- localTrendPlot + geom_hline(aes(yintercept=c(qnorm(0.1),qnorm(0.05),qnorm(0.01),qnorm(0.001),qnorm(0.0000001),qnorm(0.0000000001))),linetype="dotted",color='black',alpha=0.8)
```

##Running arithmetic average
```{r,echo=FALSE}
running_average_test <- function(inter_failure)
{
  n <- length(inter_failure)
  runningAverage <- c()
  for(i in 1:n)
  {
    sum1 <-0
    for(j in 1:i)
    {
      sum1 <- sum1 + inter_failure[j]
    }
    runningAverage[i] <- (1/i)*sum1;
  }
  runningAverage <- data.frame(c(1:length(runningAverage)),runningAverage)
  names(runningAverage) <- c("Index","Running_Average")
  return(runningAverage)
}
plot(running_average_test(IF),type="s",xlab="Failure number", ylab="Running average of interfailure times",main="Running arithmetic average test")
```

#Tab2: Set Up and Apply Models
```{r, echo=FALSE}
source('~/Downloads/srt-3.core-master/models/DSS/DSS_BM_FT.R')
source('~/Downloads/srt-3.core-master/models/GO/GO_BM_FT.R')
source('~/Downloads/srt-3.core-master/models/JM/JM_BM.R')
source('~/Downloads/srt-3.core-master/models/GM/GM_BM.R')
source('~/Downloads/srt-3.core-master/models/Wei/Wei_NM_FT.R')
```

## Cumulative failures - JM, GM, GO, DSS, and Weibull
```{r, echo=FALSE}
#change line 115 if Wei_NM_FT.R to names(params) <- c("Wei_aMLE","Wei_bMLE","Wei_cMLE")

#names(hxy) <- c("DSS","GO","JM","GM","Wei")
  #   hxy <- c(1:5)
  #   if(!is.na(DSS_BM_MLE(FT))){hxy[1] <- DSS_MVF(DSS_BM_MLE(FT),d)[,2]}else{hxy[1]<-0}
  #   if(!is.na(GO_BM_MLE(FT))){hxy[2]<-GO_MVF(GO_BM_MLE(FT),d)[,1]}else{hxy[2]<-0}
  #   if(!is.na(JM_BM_MLE(IF))){hxy[3]<-JM_MVF(JM_BM_MLE(IF),d)[,1]}else{hxy[3]<-0}
  #   if(!is.na(GM_BM_MLE(IF))){hxy[4]<-GM_MVF(GM_BM_MLE(IF),d)[,2]}else{hxy[4]<-0}
  #   if(!is.na(Wei_NM_MLE(FT))){hxy[5]<-Wei_MVF(Wei_NM_MLE(FT),d)[,2]}else{hxy[5]<-0}
  # hxy

#Exclude models with non-convergence and make the below code reactive.
hxy <- data.frame(DSS_MVF(DSS_BM_MLE(FT),d)[,2],GO_MVF(GO_BM_MLE(FT),d)[,1],JM_MVF(JM_BM_MLE(IF),d)[,1],GM_MVF(GM_BM_MLE(IF),d)[,2],Wei_MVF(Wei_NM_MLE(FT),d)[,2])
ntrees <- length(hxy)
plot(FT, FN, type="n", xlab="Cumulative test time",
  	ylab="Cumulative failures" ) 
colors <- rainbow(ntrees) 
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, FN, type="s") 
for (i in 1:ntrees) { 
  lines(FT, hxy[,i], type="l", col=colors[i]) 
} 
title("Cumualtive failures vs. cumualtive test time")
legend("topright", legend=c("DSS","GO","JM","GM","Wei"), 1:ntrees+1, cex=0.8, col=colors)#legend text and lines should match
```

## Times between failures or MTTF
```{r,echo=FALSE}
hxy <- data.frame(DSS_MTTF(DSS_BM_MLE(FT),d)[,2],GO_MTTF(GO_BM_MLE(FT),d)[,2],JM_MTTF(JM_BM_MLE(IF),d)[,2],GM_MTTF(GM_BM_MLE(IF),d)[,2],Wei_MTTF(Wei_NM_MLE(FT),d)[,2])
ntrees <- length(hxy)
plot(FT, IF, type="n", xlab="Cumulative test time",
  	ylab="Times between failures" ) 
colors <- rainbow(ntrees) 
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, IF, type="s") 
for (i in 1:ntrees) { 
  lines(FT, hxy[,i], type="l", col=colors[i]) 
} 
title("Times between failures vs. cumualtive test time")
legend("topright", legend=c("DSS","GO","JM","GM","Wei"), 1:ntrees+1, cex=0.8, col=colors)#legend text and lines should match
```

## Failure intensity
```{r,echo=FALSE}
hxy <- data.frame(DSS_FI(DSS_BM_MLE(FT),d)[,2],GO_FI(GO_BM_MLE(FT),d)[,2],JM_FI(JM_BM_MLE(IF),d)[,2],GM_FI(GM_BM_MLE(IF),d)[,2],Wei_FI(Wei_NM_MLE(FT),d)[,2])
ntrees <- length(hxy)
plot(FT, IF, type="n", xlab="Cumulative test time",
  	ylab="Failure intensity" ) 
colors <- rainbow(ntrees) 
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, IF, type="s") 
for (i in 1:ntrees) { 
  lines(FT, hxy[,i], type="l", col=colors[i]) 
} 
title("Failure intensity vs. cumualtive test time")
legend("topright", legend=c("DSS","GO","JM","GM","Wei"), 1:ntrees+1, cex=0.8, col=colors)#legend text and lines should match
```

##Reliability Growth
```{r,echo=FALSE}
#DSS_R_growth(DSS_BM_MLE(FT),d,600)[,2]#600 is the delta value - mission time - should make it reactive
hxy <- data.frame(DSS_R_growth(DSS_BM_MLE(FT),d,600)[,2],GO_R_growth(GO_BM_MLE(FT),d,600)[,2],JM_R_growth(JM_BM_MLE(FT),d,600)[,2],GM_R_growth(GM_BM_MLE(FT),d,600)[,2],Wei_R_growth(Wei_NM_MLE(FT),d,600)[,2])
ntrees <- length(hxy)
plot(FT, seq(from=0, to=1, by=1/(length(FT)-1)), type="n",xlab="Cumulative test time",
  	ylab="Reliability growth" ) #Remove this line
colors <- rainbow(ntrees) 
linetype <- c("p","l","o","b","c","s","S","h")  
lines(FT, IF, type="s") 
for (i in 1:ntrees) { 
  lines(FT, hxy[,i], type="l", col=colors[i]) 
} 
title("Reliability growth vs. cumualtive test time")
legend("topright", legend=c("DSS","GO","JM","GM","Wei"), 1:ntrees+1, cex=0.8, col=colors)#legend text and lines should match
```

#Tab3: Query Model Results
```{r,echo=FALSE}
source('~/Downloads/srt-3.core-master/utility/prediction/Detailed_prediction.R')
predTable <- matrix(NA, nrow = 5, ncol = 3)
rownames(predTable) <- c("DSS","GO","JM","GM","Wei")
colnames(predTable) <- c("Time to achieve specified reliability","Expected number of failures","Expected time to N failure")
predTable[,1] <- c(get_reliability_t("DSS",DSS_BM_MLE(FT),0.9,600,last(FT),1),get_reliability_t("GO",GO_BM_MLE(FT),0.9,600,last(FT),1),get_reliability_t("JM",JM_BM_MLE(IF),0.9,600,last(IF),1),get_reliability_t("GM",GM_BM_MLE(IF),0.9,600,last(IF),1),get_reliability_t("Wei",Wei_NM_MLE(FT),0.9,600,last(FT),1))
predTable[,2] <- c(get_prediction_k("DSS",DSS_BM_MLE(FT),10,last(FT),length(FT)),get_prediction_k("GO",GO_BM_MLE(FT),10,last(FT),length(FT)),get_prediction_k("JM",JM_BM_MLE(IF),10,last(FT),length(FT)),get_prediction_k("GM",GM_BM_MLE(IF),10,last(FT),length(FT)),get_prediction_k("Wei",Wei_NM_MLE(FT),10,last(FT),length(FT)))
predTable[,3] <- c(get_prediction_t("DSS",DSS_BM_MLE(FT),1,last(FT),length(FT)),get_prediction_t("GO",GO_BM_MLE(FT),1,last(FT),length(FT)),get_prediction_t("JM",JM_BM_MLE(IF),1,last(FT),length(FT)),get_prediction_t("GM",GM_BM_MLE(IF),1,last(FT),length(FT)),get_prediction_t("Wei",Wei_NM_MLE(FT),1,last(FT),length(FT)))#The table can only handle a single value
kable(predTable)
```

#Tab4: Evaluate Models
```{r,echo=FALSE}
source('~/Downloads/srt-3.core-master/utility/metrics/GOF.R')
GOFTable <- matrix(NA, nrow = 5, ncol = 2)
rownames(GOFTable) <- c("DSS","GO","JM","GM","Wei")
colnames(GOFTable) <- c("AIC","PSSE")
GOFTable[,1] <- c(aic(2,DSS_lnL(FT,DSS_BM_MLE(FT))),aic(2,GO_lnL(FT,GO_BM_MLE(FT))),aic(2,JM_lnL(IF,JM_BM_MLE(IF))),aic(2,GM_lnL(IF,GM_BM_MLE(IF))),aic(3,Wei_lnL(FT,Wei_NM_MLE(FT))))
GOFTable[,2] <- c(psse("DSS",d,DSS_BM_MLE(FT),0.9),psse("GO",d,GO_BM_MLE(FT),0.9),psse("JM",d,JM_BM_MLE(IF),0.9),psse("GM",d,GM_BM_MLE(IF),0.9),psse("Wei",d,Wei_NM_MLE(FT),0.9))#Need to verify these numbers
kable(GOFTable)
```

